The supernova-regulated ISM - III. Magnetic fields in the multi-phase gas

### 2015-03-10 paper.tex
Removed include{mhdruns}
Clipped 3D plots to fit width

%-----------------------------------------------------------------------------
  \begin{figure*}
  \angle{90}
  \centering
  \hspace{-1.25cm}
  \includegraphics[width=0.3965\linewidth]{fig/b310c.png}\hspace{-1.15cm}
  \includegraphics[width=0.3965\linewidth]{fig/b310w.png}\hspace{-1.15cm}
  \includegraphics[width=0.3965\linewidth]{fig/b310h.png}
  \hspace{-1.25cm}
  \caption[Volume snapshots of $\vect{B}$ by phase for Model~$\Ompa$]{
  Vector plots of the magnetic field $\vect{B}$ {\text{(a)}} in the cold phase
  {\text{(b)}} the warm phase and {\text{(c)}} the hot phase.
  Field directions are indicated by arrows and strength by their thickness.
  The colour of the arrows indicates the strength of the
  azimuthal ($y$) component (colour bar on the right).
  The background shading illustrates the density of the ISM.
  \label{fig:b3box}}
  \end{figure*}
%-----------------------------------------------------------------------------

@@

\input{mhdruns}
%end FAG
%-----------------------------------------------------------------------------

>>>>

%-----------------------------------------------------------------------------
  \begin{figure*}
  \centering
  \hspace{-3.5cm}
  %\includegraphics[angle=90, width=0.5\linewidth]{fig/b310h.png}\vspace{-1.15cm}\\
  %\includegraphics[angle=90, width=0.5\linewidth]{fig/b310w.png}\vspace{-1.15cm}\\
  %\includegraphics[angle=90, width=0.5\linewidth]{fig/b310c.png}
  \includegraphics[angle=0, trim=0.5cm 0cm 2cm 0cm, clip=true, totalheight=0.33\textheight]{fig/b310c.png}\hspace{-1.15cm}
  \includegraphics[angle=0, trim=0.5cm 0cm 2cm 0cm, clip=true, totalheight=0.33\textheight]{fig/b310w.png}\hspace{-1.15cm}
  \includegraphics[angle=0, trim=0.5cm 0cm 2cm 0cm, clip=true, totalheight=0.33\textheight]{fig/b310h.png}
  \hspace{-4.5cm}
  \caption[Volume snapshots of $\vect{B}$ by phase for Model~$\Ompa$]{
  Vector plots of the magnetic field $\vect{B}$ {\text{(a)}} in the cold phase
  {\text{(b)}} the warm phase and {\text{(c)}} the hot phase.
  Field directions are indicated by arrows and strength by their thickness.
  The colour of the arrows indicates the strength of the
  azimuthal ($y$) component (colour bar on the right).
  The background shading illustrates the density of the ISM.
  \label{fig:b3box}}
  \end{figure*}
%-----------------------------------------------------------------------------

@@

%end FAG
%-----------------------------------------------------------------------------
